Designing Modular Software: A Case Study in Introductory Statistics

### 2016-12-09 jcgs-paper-2016/response.Rmd

---
title: "Response to third review"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: pdf_document
---

# Associate Editor

1. two brief comments from one reviewer should both be addressed

    **We have addressed these two comments**

2. from other reviewer, address the minor fixes

    **As noted in the comments in this document, we have addressed what we felt were the more minor fixes**

3. remove the comments about Radiant being "inundated with more features than necessary"

    **This comment has been removed**

4. a sentence or two more on comparison with Radiant, e.g., mention Radiant's less focus on *extensibility* (if that is true)

    **We have extended the comparison with Radiant by noting Radiant's more extensive functionality and the differences in the goals of each**

@@

# Reviewer 2

5. Page 3 re iNZight Lite. The model fitting module in iNZight writes R reproducible code (and has since its inception) and it all will eventually so tone back this criticism a little. Given the sentence that comes before, I think this sentence could be just deleted without weakening the motivation for this paper and project.

    **We have clarified the differences in reproducibility as requested**

6. Figure 3: I take it that the contents of helper.R, libraries.R, ... get sucked in to populate/form server.R. This could be made clearer (or this misconception countered).

    **We have updated the figure caption to better explain how these files populate both the server and the ui definitions.**

# Reviewer 3

7. p1. Not sure when this package was originally written, but R Core Team 2014 probably needs to be updated to 2016.

    **We have updated the citation for R**

8. I don't follow the logic here. Perhaps give an example of which platform does not support them.

    **We have provided an example of this in the paper (Microsoft Excel and JMP are not supported on Linux)**

9. p2. "RStudio and Inc. 2014": the .bib entry should be author = {{RStudio, Inc.}}

    **Fixed**

10. perhaps change to "even if the instructors use R in their own work"?

    **Fixed**

11. p9. wilcoxon -> Wilcoxon (also on following pages)

    **We have corrected this throughout the paper**

12. p10. I think pseudocode suffices in Figure 3; no need to put actual code in it. In server.R, typically the arguments are input, output, session, and I'm not sure if session, input, output is the same.

    **We have updated the order of the arguments in figure 3.**

13. p15. Okay, interpolate() was explained in detail here. Then p12 should have referenced this section.

    **We have referenced this section on page 12**

### 2016-12-09 jcgs-paper-2016/paper.Rmd
New response and small edits

Modern web technologies have enabled a new generation of software packages that reside solely on the web, which eliminates the issue of local installation and helps abstract away some of the more challenging programming aspects of working directly with R. Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. Several recent software packages have built upon Shiny to provide a web-based system based on R. One such package is iNZight Lite [@inzight] which attempts to expose students to data analysis without requiring programming knowledge. inZight Lite is currently partially but not fully reproducible. Another package is called Radiant [@radiant], which is a web-based application with the aim of furthering business education and financial analysis. While the application is modular and extensible, it does require local installation and hosting. An overview of the comparison between the features of these statistical software packages is presented in Table \ref{tab:compare}. Partial fulfillment of requirements is noted in the table, as well as a measure of the complexity of functionality offered by default. For example, `R` does have an associated Graphical User Interface (GUI), however this interface is very limited, thus only partially fulfilling the behavior of a GUI.

>>>>

Modern web technologies have enabled a new generation of software packages that reside solely on the web, which eliminates the issue of local installation and helps abstract away some of the more challenging programming aspects of working directly with R. Upon the release of RStudio's Shiny [@shiny] it became easier for an R-based analysis to be converted to an interactive web application. Several recent software packages have built upon Shiny to provide a web-based system based on R. One such package is iNZight Lite [@inzight] which attempts to expose students to data analysis without requiring programming knowledge. inZight Lite is currently partially but not fully reproducible. Another package is called Radiant [@radiant], which is a very promising web-based application with the aim of furthering business education and financial analysis. While the application is modular and extensible, it does require local installation and hosting. Radiant is a business analytics platform with a host of functionality, while **intRo** focuses on being a simple and extensible web tool for learning. An overview of the comparison between the features of these statistical software packages is presented in Table \ref{tab:compare}. Partial fulfillment of requirements is noted in the table, as well as a measure of the complexity of functionality offered by default. For example, `R` does have an associated Graphical User Interface (GUI), however this interface is very limited, thus only partially fulfilling the behavior of a GUI.
